Next Trippy Structures\thanks{Supported by organization x.}

### 2019-07-29 paper.tex
Fix subcaption errors

\usepackage{enumerate}
\usepackage{marginnote}
\usepackage[linesnumbered,commentsnumbered,boxed]{algorithm2e}
\usepackage{amsmath}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage[margin=0pt,skip=1pt]{subcaption}
\usepackage{xcolor}
\usepackage{fixltx2e}

@@

@@

\begin{table}
    \caption{Space requirements for the \texttt{CSA} (a) and the \texttt{WM} (b) from \ttctr}
    \label{tab:ttctr}
    \begin{subtable}[t]{.30\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (a)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|}
        \hline
        t$_\Psi$ & bps & Size (MiB) \\
         \hline
        32 & 7.288 & 30.91 \\
        128 & 6.069 & 25.74 \\
        512 & 5.761 & 24.43 \\
        \hline
    \end{tabular}
    \end{subtable}%
    \begin{subtable}[t]{.40\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (b)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|}
        \hline
        Bitvector & bps & Size (MiB) \\
         \hline
        RG32 & 14.438 & 44.02 \\
        RRR32 & 13.478 & 41.09 \\
        RRR64 & 12.79 & 38.99 \\
        RRR128 & 12.446 & 37.94 \\
        \hline
    \end{tabular}
    \end{subtable}
\end{table}

@@

\begin{table}
    \caption{Space requirements for the \texttt{CSA} (a), the \texttt{WMJ} (b) and the \texttt{WML} (c) from \ctr}
    \label{tab:ctr}
    \begin{subtable}[t]{.28\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (a)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|}
        \hline
        t$_\Psi$ & bps & Size (MiB) \\
         \hline
        32 & 6.956 & 29.50 \\
        128 & 5.727 & 24.29 \\
        512 & 5.417 & 22.97 \\
        \hline
    \end{tabular}
    \end{subtable}
    \begin{subtable}[t]{.38\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (b)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|}
        \hline
        Bitvector & bps & Size (MiB) \\
         \hline
        RG32 & 14.438 & 61.23 \\
        RRR32 & 13.419 & 56.91 \\
        RRR64 & 12.732 & 53.99 \\
        RRR128 & 12.388 & 52.53 \\
        \hline
    \end{tabular}
    \end{subtable}
    \begin{subtable}[t]{.30\linewidth}
    \vspace{-12pt}
    \caption{\footnotesize (c)}
    \vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|}
        \hline
        Bitvector & bps & Size (MiB) \\
         \hline
        RG32 & 4.778 & 20.26 \\
        RG32 & 2.338 & 9.91 \\
        RG64 & 2.18 & 9.24 \\
        RG128 & 2.103 & 8.92 \\
        \hline
    \end{tabular}
    \end{subtable}%
\end{table}

@@

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/start.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/end.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{start\_X$_{LT}$} (a) and \texttt{end\_X$_{LT}$} (b) queries, with all variants. Note the logarithmic scale for the y axis in (b)}
\label{fig:start}
\end{figure}

@@

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy0.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy1.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (a) and starting time (b) restrictions}
\label{fig:xy0}
\end{figure}

@@

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy2.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy3.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (a) and starting time (b) restrictions with a fixed ending time restriction}
\label{fig:xy2}
\end{figure}

@@

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/board.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/board_t.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{board\_X$_{LT}$} queries, with all variants (a) and also with all variants of \acumm~(b). Note the logarithmic scale in (b), as well as the measurements in nanoseconds}
\label{fig:board}
\end{figure}

>>>>

\usepackage{enumerate}
\usepackage{marginnote}
\usepackage[linesnumbered,commentsnumbered,boxed]{algorithm2e}
\usepackage{amsmath}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{caption}
\usepackage[margin=0pt,skip=1pt]{subcaption}
\captionsetup{compatibility=false}
\usepackage{xcolor}
\usepackage{fixltx2e}

@@

\ojo{sin acabar}
Storing and efficiently analyzing large datasets of passenger's trips over public transportation networks brings the ability to gather the actual user's demands and consequently sets the basis to balance both the offer and such demands. We show that the use of compact data structures makes up a promising representation of passenger's trips that not only permits us to reduce the space needed to store them, but also provides efficient access operations at query time.

In this work, we propose a solution based on two complementary representations, named \acumm~and~\ttctr. The former excels at operations XXX, whereas the later excels at operations YYY. In addition, we propose a variant of \ttctr\ named \ctr\ that performs better at operations XXX at the cost of losing performance at ... with an alternative for the later called \ctr. Overall, with our representation we were able to represent a dataset of ten million trips in around 100 MB, while supporting a wide range of queries in the order of microseconds. \ojo{non sei se se pode explicar a grandes rasgos e en pouco espazo que fan as 3 tecnicas, e cales son as suas vantaxes}

@@

\begin{table}
    \caption{Space requirements for the \texttt{CSA} (a) and the \texttt{WM} (b) from \ttctr}
    \label{tab:ttctr}
    \begin{subtable}[t]{.30\linewidth}
    \vspace{-12pt}
    \caption{}
    %\vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|}
        \hline
        t$_\Psi$ & bps & Size (MiB) \\
         \hline
        32 & 7.288 & 30.91 \\
        128 & 6.069 & 25.74 \\
        512 & 5.761 & 24.43 \\
        \hline
    \end{tabular}
    \end{subtable}%
    \begin{subtable}[t]{.40\linewidth}
    \vspace{-12pt}
    \caption{}
    %\vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|}
        \hline
        Bitvector & bps & Size (MiB) \\
         \hline
        RG32 & 14.438 & 44.02 \\
        RRR32 & 13.478 & 41.09 \\
        RRR64 & 12.79 & 38.99 \\
        RRR128 & 12.446 & 37.94 \\
        \hline
    \end{tabular}
    \end{subtable}
\end{table}

@@

\begin{table}
    \caption{Space requirements for the \texttt{CSA} (a), the \texttt{WMJ} (b) and the \texttt{WML} (c) from \ctr}
    \label{tab:ctr}
    \begin{subtable}[t]{.28\linewidth}
    \vspace{-12pt}
    \caption{}
    %\vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|}
        \hline
        t$_\Psi$ & bps & Size (MiB) \\
         \hline
        32 & 6.956 & 29.50 \\
        128 & 5.727 & 24.29 \\
        512 & 5.417 & 22.97 \\
        \hline
    \end{tabular}
    \end{subtable}
    \begin{subtable}[t]{.38\linewidth}
    \vspace{-12pt}
    \caption{}
    %\vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|}
        \hline
        Bitvector & bps & Size (MiB) \\
         \hline
        RG32 & 14.438 & 61.23 \\
        RRR32 & 13.419 & 56.91 \\
        RRR64 & 12.732 & 53.99 \\
        RRR128 & 12.388 & 52.53 \\
        \hline
    \end{tabular}
    \end{subtable}
    \begin{subtable}[t]{.30\linewidth}
    \vspace{-12pt}
    \caption{}
    %\vspace{-12pt}
    \begin{tabular}[t]{|l|l|r|}
        \hline
        Bitvector & bps & Size (MiB) \\
         \hline
        RG32 & 4.778 & 20.26 \\
        RG32 & 2.338 & 9.91 \\
        RG64 & 2.18 & 9.24 \\
        RG128 & 2.103 & 8.92 \\
        \hline
    \end{tabular}
    \end{subtable}%
\end{table}

@@

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/start.eps}
\vspace{-12pt}
\caption{}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/end.eps}
\vspace{-12pt}
\caption{}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{start\_X$_{LT}$} (a) and \texttt{end\_X$_{LT}$} (b) queries, with all variants. Note the logarithmic scale for the y axis in (b)}
\label{fig:start}
\end{figure}

@@

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy0.eps}
\vspace{-12pt}
\caption{}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy1.eps}
\vspace{-12pt}
\caption{}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (a) and starting time (b) restrictions}
\label{fig:xy0}
\end{figure}

@@

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy2.eps}
\vspace{-12pt}
\caption{}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy3.eps}
\vspace{-12pt}
\caption{}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (a) and starting time (b) restrictions with a fixed ending time restriction}
\label{fig:xy2}
\end{figure}

@@

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/board.eps}
\vspace{-12pt}
\caption{}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/board_t.eps}
\vspace{-12pt}
\caption{}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{board\_X$_{LT}$} queries, with all variants (a) and also with all variants of \acumm~(b). Note the logarithmic scale in (b), as well as the measurements in nanoseconds}
\label{fig:board}
\end{figure}
